\documentclass{resume}
\usepackage[left=0.2 in,top=0.2in,right=0.4 in,bottom=0.2in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{soul}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mohammad Muid Uddin Chowdhury} % Your name
\address{\\ \textbf{Address:} Chattogram, Bangladesh \\ \textbf{Tele-Phone:} +8801843771524 \\ \textbf{E-Mail:} \href{mailto:umuidrahi@gmail.com} {\ul{umuidrahi@gmail.com}
}
}
\address{\\ \textbf{LinkedIn:} \href{https://www.linkedin.com/in/muid-uddin/}{\ul{/in/muid-uddin}} \\ \textbf{GitHub:}
\href{https://github.com/muid-uddin-chowdhury}{\ul{muid-uddin-chowdhury}} \\ \textbf{Website:}
\href{https://sites.google.com/view/muid-uddin-chowdhury/home}{\ul{Muid Uddin Chowdhury}
}
}
\begin{document}
\begin{rSection}{Research Interest}
\normalfont Machine Learning, Artificial Intelligence, Data Science, Signal Processing, Image Processing, Computer Vision, Wireless Communication, Semiconductor Physics, and Very Large Scale Integrated Circuits.
\end{rSection}

\begin{rSection}{Education}
{\normalfont Bachelor of Science (B.Sc) in Electronics and Telecommunication Engineering. \hfill \textit{February 2017 - June 2022}\\ 
\normalfont Chittagong University of Engineering and Technology (CUET), Chattogram, Bangladesh. \\
\normalfont CGPA: 3.24 (On a scale of 4) \\
\textit{Last Term CGPA: 3.65 (On a scale of 4)}
\end{rSection}

\begin{rSection}{Research Experiences}
\normalfont Undergraduate thesis on "Delay Optimization of an 8-bit ALU by using Full Swing Gate Diffusion Input Technique" under the supervision of Mr.Mohammad Anisur Rahaman.\\ 
\textit{January 2021 – June 2022}
 \end{rSection}

\begin{rSection}{Technical Skills}
\normalfont 1) Fluent in Matlab, Python, Java, C, and C++. \\
2) Hands-on experience in Cadence Virtuoso. \\
3) Skilled in Microsoft Office Suite and LaTex.
\end{rSection}

\begin{rSection}{CERTIFICATIONS}
\begin{tabular}{l l}
Machine Learning & Neural Networks and Deep Learning \\
\normalfont Stanford University  & \normalfont Coursera\\
\normalfont Credential ID 2J4J32L77KZK & \normalfont Credential ID E4D9DL4J775T
\end{tabular}
\end{rSubsection} 

\begin{rSection}{APTITUDE TESTS}
International English Language Testing System(IELTS) \normalfont \textit{(Taken on 17 March 2023)}
\begin{center}
\begin{tabular}{|c |c |c |c |c|}\hline
Overall Band Score & Listening & Speaking & Reading & Writing \\
\hline
\normalfont 7 & \normalfont 8 & \normalfont 7 & \normalfont 7 & \normalfont 6 \\
\hline
\end{tabular} \\
\end{center}

\textbf{Graduate Record Examination(GRE)} \normalfont \textit{(Taken on 28 November 2022)}
\begin{center}
\begin{tabular}{|c |c |c |c|}\hline
Test Score & Verbal & Quant & AWA \\
\hline
\normalfont 302 & \normalfont 143 & \normalfont 149 & \normalfont 3 \\
\hline
\end{tabular}\\
\end{center}
\end{rSection} 

\begin{rSection}{PROJECTS}

\begin{rSubsection}{}{} {} {} 
\item 1) Frequency Meter by using Arduino Uno. \\
\normalfont The frequency from a power generator is calculated by using Arduino Uno and an 8-digit display. \\ 

\item \textbf{2) Arduino, Android, and Wi-Fi module Nodemcu ESP8266-based Smart door lock.} \\
\normalfont By scanning a QR code, a URL is found, and by giving a proper password and a username, a smart door can be unlocked. \\

\item \textbf{3) Automatic Traffic Light control system by PIC 16F877A.} \\
\normalfont By giving a specific delay time, Red, Green, and Blue lights operate for a specific amount of time.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{LEADERSHIP EXPERIENCES} 
1) General Secretary, \normalfont Chittagong Math Circle (2019-2021). \\
\textbf{2) Financial Secretary,} \normalfont Chittagong Math Circle (2017-2019). \\
\textbf{3) Assistant Education and Research Secretary,} \normalfont Chittagong Student Forum – CUET (2020-2021). \\
\textbf{4) President,} \normalfont Chittagong Government High School Math Club (2013-2014). \\
\textbf{5) Academic Team Member,} \normalfont Bangladesh Mathematical Olympiad.

\end{rSection}

\begin{rSection}{Linguistic Proficiency}
\textbf{English:} \normalfont Fluent in speaking and writing.\\
\textbf{Bangla:} \normalfont Native Language.  
\end{rSection}

\begin{rSection}{REFERENCES}
\begin{tabular}{l l}
Dr. Md. Azad Hossain & Mohammad Anisur Rahman \\
Professor, & Assistant Professor,\\
\normalfont Department of Electronics and & \normalfont Department of Electronics and \\
\normalfont Telecommunication Engineering, & \normalfont Telecommunication Engineering \\
\normalfont Chittagong University of Engineering & \normalfont Chittagong University of Engineering \\
\normalfont and Technology & \normalfont and Technology \\
\normalfont \href{mailto:azad98@gmail.com} E-mail: \textit{\ul{azad98@gmail.com}} & \normalfont\href{mailto:anisur.rahaman@cuet.ac.bd} E-mail: \textit{\ul{anisur.rahaman@cuet.ac.bd}} \\
\normalfont Tele-phone: +8801783756981 & \normalfont Tele-phone: +880187879096
\end{tabular}
\end{rSection}    
\end{rSection}

\end{document}
